A Survey of Range-Only SLAM Techniques and Sensors

### 2018-02-27 Paper.tex
Revert "Random Fixes to Body"
This reverts commit bf1d10d3d2648868501859948f351b17aa3b1ecc.

	\section{range only sensors}
	\label{range only sensors}
		There are a variety of sensors which can be utilized as range beacons for RO-SLAM. These range sensors refer to any device which involves a signal transmission that can be used for the range estimation without line of sight. The most popular sensors can largely be broken down into two categories: acoustic based and radio frequency based. These beacons serve as landmarks within larger SLAM algorithms. The following section surveys the different types of sensors which can be utilized as range beacons.

@@

			Ultra-wideband radios are another popular choice. One attractive feature of currently used ultra-wide band transmitters and receivers is the ability resolve multipath error ,which is a common obstacle with indoor environments, without the use of extensive algorithms. \cite{Gezici2005} presents an analysis of time of arrival based localization estimations with ultra-wide band.

			 \cite{Baronti2007}, \cite{Khanafer2014}, \cite{Akyildiz2002}, and \cite{Xia2011} each present surveys relating to wireless sensor networks.  \cite{Baronti2007} and \cite{Akyildiz2002} both provide very well developed surveys that discuss hardware, protocols, standards, security, energy efficiency and much more. \cite{Baronti2007} specifically focuses on state of the art 802.15.4 and ZigBee standards. \cite{Xia2011} examines the limitations of original IEEE 802.15.4 MAC and reviews adaptive methods that have been used to overcome these limitations. \cite{Khanafer2014} specifically survey methods meant to improve the performance of IEEE 802.15.4 MAC protocol.

>>>>

	\section{range only sensors}
	\label{range only sensors}
		There are a variety of sensors which can be utilized as range beacons for RO-SLAM. These range sensors refer to any device which involves a signal transmission that can be used for the range estimation without line of sight. The most popular sensors can largely be broken down into two categories: acoustic based and radio frequency based. These two types of sensors both rely on the same principles for measuring distances, which is either by signal time of flight, or signal attenuation through propagation through each respective medium. These beacons serve as landmarks within larger SLAM algorithms. The following section surveys the different types of sensors which can be utilized as range beacons.

@@

			 Another popular wireless standard often used in wireless ranging and localization applications is IEEE 802.15.4, which has been largely popularized by the ZigBee protocol. In contrast with IEEE 802.11 WiFi standards, 802.15.4 is focused on shorter-ranged, low power peer-to-peer networks, thus making it a widely used protocol in Wireless Sensor Networks (WSN).  \cite{Baronti2007}, \cite{Khanafer2014}, \cite{Akyildiz2002}, and \cite{Xia2011} each present surveys relating to WSNs. \cite{Baronti2007} and \cite{Akyildiz2002} both provide very well developed surveys that discuss hardware, protocols, standards, security, energy efficiency and much more. \cite{Baronti2007} specifically focuses on wireless sensors utilizing ZigBee standards. \cite{Xia2011} examines the limitations of original IEEE 802.15.4 MAC and reviews adaptive methods that have been used to overcome these limitations. \cite{Khanafer2014} specifically survey methods meant to improve the performance of IEEE 802.15.4 MAC protocol.

			 Ultra-wideband (UWB) radios are another popular choice. One attractive feature of currently used ultra-wide band transmitters and receivers is the ability resolve multipath error ,which is a common obstacle with indoor environments, without the use of extensive algorithms due to its use of multiple frequencies across a large bandwidth. \cite{Gezici2005} presents an analysis of time of arrival based localization estimations with ultra-wide band.
